An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-09-28 scagnostics.Rmd
organisation of topics

---
title: An investigation into using scagnostics interesting projections of high-dimensional data

@@

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = FALSE, external = TRUE, dev = "pdf",
  fig.height = 5, fig.width = 8, out.width = "\\textwidth"
)
```

@@

A large number of projection pursuit indices have been developed [@f87] [@CBC92] [@Lee05] [@AHC02] [@CEM:CEM2568] [@JS87] [@5508437]. Many of these are developed to detect departure from multivariate normal, which includes clusters or outliers. Some have been developed to detect separations between known groups [REF]. Less work has been done on indexes to find nonlinear dependence between variables.

@@

Criteria for a good index
  - smoothness
  - speed
  - fine and broad structure detection
Simulation study
  - example data 
  - sample size, and other factors used
Overview procedures 
  - look at index values of pairs of variables
  - tour betwen pairs of variables
  - optimisation path

@@

>>>>

---
title: An investigation into using scagnostics to find interesting projections of high-dimensional data

@@

```{r initial, echo = FALSE, cache = TRUE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = FALSE, external = TRUE, dev = "pdf",
  fig.height = 5, fig.width = 8, out.width = "\\textwidth"
)
```

@@

A large number of projection pursuit indices have been developed, to detect departure from multivariate normal, which includes clusters or outliers or separations between known groups (e.g. @f87, @CBC92, @Lee05, @AHC02, @CEM:CEM2568, @JS87, @5508437).  Less work has been done on indexes to find nonlinear dependence between variables.

@@

Criteria for a good index

  - smoothness
  - speed
  - fine and broad structure detection

Simulation study

  - example data 
  - sample size, and other factors used

Overview procedures

  - look at index values of pairs of variables
  - tour betwen pairs of variables
  - optimisation path

@@

<!-- 
Table and figure captions need to have three components: (1) what is the plot about, (2) specific details of plot, like what type of display and how variables are mapped, (3) the most important thing that the reader should learn.

Be sure to cite R, as well as packages used in the work.
-->
